\vfill A Survey of Web Testing Frameworks and a Workflow for Testing Javascript Applications

### 2014-05-10 Paper/paper.tex
Removal of 'you'

In the very beginning, web applications were easy to write and test because the only code was straight HTML with a common set of HTML tags. It didn't matter what browser you viewed the content in because it was always a home computer rendering plain HTML. As time progressed individual browsers began offering additional features and web applications became more rich but harder to test because the developer would need to run their code on a couple different browsers to make sure they all behaved similarly. In today's technological world, it is nearly impossible to run one's web application on all of the possible browser versions, configurations, and platforms that are available. Web applications are on home computers, phones, tablets, MP3 players, refrigerators \cite{SamsungFridge}, and a variety of other devices of varying sizes and capabilities. As a developer, you want to target as many of those platforms as possible with a single code-base to save yourself time and effort. A naive developer might just release an application on all platforms and hope for the best, but releasing on all platforms without testing will likely drive consumers away if the application fails on their given platform.

@@

\subsubsection{Availability}
Web application are available anywhere there's internet. No need to install anything on a given device most of the time. Due to the ever-increasing popularity of mobile devices, most applications have both mobile and full versions of their software and so the application is ``with you'' all the time.

\subsubsection{Multi-platform}
Very similar to the availability strength, web applications are platform independent. Whether you're on your phone, tablet, laptop, or PC, the application only requires a web browser with certain functionality and in this day and age all devices come equipped with browsers that should have no problems.

@@

\subsubsection{What is the Client-side Portion?}
First, we'll address what a client is. The simple answer is: You. Your phone, computer, tablet, or other device communicating with a given website or application is the client. More specifically, the browser or service you're using to communicate with the web is the client.

@@

\subsubsection{Unit Testing}
Unit testing is the testing of specific functions and functionality. Generally this means the testing of individual functions but can extend to a set of functions that produce a single module of functionality. What sets Unit Testing apart from other types of testing is that tests focus on one portion of the code or system rather than interactions between modules or the entire system.

@@

\todo{Wrap up?}

\subsubsection{Continuous Integration}
Continuous Integration (CI), in the context of testing, also known as Continuous Testing, is the term for a piece of software or service that continually runs tests on your code as you develop. The purpose of this is to make sure that new code is not breaking old tests and that new code is passing any tests you've written for it prior to writing it. This is invaluable feedback because you can see if you're making progress in the right direction as you write code, as opposed to a situation in which you finish coding and find out you made a bad assumption or decision early on.

One of the most important aspects of a good piece of CI software is that it is automatic. There should be no need for a developer to do anything besides ``turn it on'' and start coding. As soon as a tool, CI or otherwise, requires more than one or two interactions to run, it becomes more of a nuisance and less of an asset.

\subsubsection{Acceptance Testing}
Acceptance testing is testing to confirm that your product meets a certain specification. Often in the terms of software this is making sure that your software meets an SRS (Software Requirements Specification) or a customer's outlined expectations. Often this testing is performed by the user of the software or that customer that ordered the software, rather than the developers.

@@

\subsection{Assumptions and Requirements}
In order to more thoroughly vet the many testing frameworks we came across, we had a number of assumptions about the projects we'd be looking at and requirements for those framework.
%- Node.js server because it's JS, so it's testable.
%- Something to do unit testing
%- Something to do continuous integration

@@

Although there are multiple languages and tools available for creating a backing server, we chose Node.js because of it's wide use and because it is what we're most familiar with.

Javascript was chosen because it used in over 87\% of all websites. \cite{JSUsage} Web applications tend to keep track of users which most often constitutes the use of a database behind the scenes to store users and update them as necessary.

@@

@@

\subsubsection{Tool Requirements \todo{Move this section elsewhere}}
Our requirements for the selection of testing tools was relatively simple. In addition to meeting the requirements of our ``average web application'', the only other requirement was that the tool was free. What ``free'' means is that the developer would have access to at the least the minimum functionality needed to use the tool on \emph{one} application that is \emph{open-source}. What we quickly found is that web testing tools love open-source projects but are far less willing to provide free functionality to private or closed-source projects. Occasionally the cost of tools will be discussed but in general we didn't review tools that did not offer a free option.
%- Free

@@

This relates to Jasmine is the way that you write Jasmine tests. The idea behind jasmine tests is that they read, as much as possible, like english sentences. As an example, the following is a valid Jasmine test:
\begin{lstlisting}
describe("Arithmetic Test", function () {
  it("should be able to compute the addition of two numbers", function () {
    expect(1 + 2).toEqual(3);
  });

@@

Mocha also uses the ``describe -> it(\"should...\" '' pattern to create tests. There is no standard for writing expectation though, as each assertion library is likely to be slightly different.

Mocha's approach to asynchronous testing is quite a bit more straightforward than Jasmine's. In your ``it(...)'' anonymous function you pass an additional parameter called ``done'' which you then call when you know the asynchronous call has finished. This required us to edit the code we were testing to make all the async calls accept an additional callback, but it was a very small price to pay for extended testability. An example asynchronous test would look like this:
\begin{lstlisting}
describe("Asynch Mocha Test", function () {
  it("look like this", function (done) {
    myAsyncCall(param1, param2, function () {
      // This callback expected to run when async returns

@@

\subsubsection{QUnit \cite{QUnit}}
QUnit is an Assertion style framework developed by the jQuery Foundation, the makers of jQuery, an immensely popular framework for DOM manipulation and access. QUnit is a bit more developer-centered and not as ``feel-good'' as the other frameworks but has, so far, been the most easy to use and has the most thorough test reporting of any framework out of the box. Mocha and Jasmine show how many ``specs'', the ``it'' functions, have passed, which is great information, but QUnit takes it a step further and breaks down each spec into the asserts contained within:
\begin{Figure}
  \centering
  \includegraphics[width=\linewidth]{qunitrunner.png} 
  \captionof{figure}{Each individual spec is further broken down into the assertions within it.}
\end{Figure}
An interesting feature that QUnit has that we'd not seen elsewhere is the ability to specify how many assertions you expect to run in the test. This is incredibly useful for callbacks. By setting an expected number of assertions, tests can no longer fail silently just because an assertion was never run. If the QUnit test finishes and the assertion count is not what was specified, it will fail the test and let you know fewer assertions were called than expected.

@@

QUnit's handling of asynchronous tests is similar to Mocha's except instead of adding a parameter to the ``it'' function, you call the ``asyncTest'' function instead of the ``test'' function and then call ``start()'' when you finish your asynchronous tests. Example:
\begin{lstlisting}
asyncTest("Async Test", function () {
  myAsyncCall(param1, param2, function () {
    // This callback expected to run when async returns

@@

\subsubsection{Intern\cite{InternIO}}
Intern is a hybrid unit testing and browser testing framework that aims to be an all-in-one testing framework. Intern has unit testing, browser testing, and code coverage information all built into the same tool. Intern runs on its own server which give it access to the internals of your project, but caused problem with attempting to interact with a seperate server running the Node.js application. We were unable to get the browser testing portion of Intern to work because of the inability to set up cross-server communication easily and properly.

%- TDD, BDD, Object methods
Intern uses Chai.js for assertion methods but has it built-in as opposed to Mocha in which you had to get it yourself. Again, this gives the developer access to Expect, Assert, and Object testing methods.

@@

%- Code Coverage!
Intern includes configurable code coverage metrics on your tests by default. Running unit tests gives the number of lines covered (ran) by the tests. Code coverage is provided by another Javascript library, Istanbul, created by Krishnan Anantheswaran \cite{Istanbul}.

@@

Generally, all browser testing tools will be using Selenium behind the scenes and doing the housekeeping for you. This is the case for both of the web testing tools that will follow this description.

@@

Tests are written as a long chain of function calls that produce an easy-to-read series of browser events. For example, the following code segment opens a browser, goes to google.com, makes some assertions, writes ``nightwatch'' in the search box, clicks the search button, and then makes a few more assertions:
\begin{lstlisting}
module.exports = {
  "Demo test Google" : function (client) {
    client
      .url("http://www.google.com")
      .waitForElementVisible("body", 1000)
      .assert.title("Google")
      .assert.visible("input[type=text]")
      .setValue("input[type=text]", "nightwatch")
      .waitForElementVisible("button[name=btnG]", 1000)
      .click("button[name=btnG]")
      .pause(1000)
      .assert.containsText("#main", "The Night Watch")
      .end();
  }
};
\end{lstlisting}
As you can see, just reading the code line by line paints a picture of exactly what is happening and what is being checked for. The same code in straight selenium is quite a bit more verbose.

@@

Though a small feature, Nightwatch has the ability to either assert or verify tests. The difference is that assertions will stop execution while verifications will merely log the failure and continue on. Verification can be useful if you want to get an update on how many things are currently failing as opposed to having the entire test stop executing immediately after a single failure.

@@

Jenkins is a series of web pages that you set up to run on a given server. This is what it looks like:
\begin{Figure}
  \centering
  \includegraphics[width=0.95\linewidth]{jenkins.png}
\end{Figure}
Most companies give Jenkins a sub-domain on their web pages.

@@

Because Jenkins comes bare and runs on the system of your choosing, it can run any project that you set up. The downside is that there is no support out-of-the-box unless you already have the necessary compilers, interpreters, applications, and/or libraries installed on the server running Jenkins.

One of the exceptional strengths of Jenkins is that the developer is only limited by the hardware of the machine running Jenkins. Any increase in computing power will be directly usable by Jenkins. Jenkins can run as many jobs as your server can handle at one time.

@@

Jenkins is an exceptionally strong tool for CI, but requires immense overhead in setting up the environment to run your project in. However, once the server has the necessary applications and libraries, your builds and tests will run without issue. Jenkins can run an ``unlimited'' number of builds, tests, and processes with the only limiting factor the hardware that it is running on. It is also 100\% free and can connect with public and private repositories alike.

\subsubsection{Travis \cite{Travis}}
Travis is an online continuous integration framework with 29 members and 64 repositories at the time of this writing. Unlike Jenkins, Travis is all online and includes a dashboard from which you can monitor your builds and processes. Travis has a free version which is fully-featured but requires your project to be open-source and a paid version which gives you more processing power and access to private repositories.

Travis comes with internal support for eleven different languages including Node.JS, Ruby, Java, Python, and more. Travis has incredibly thorough documentation and a wealth of built-in services to work with your project if needed. Services like databases, notifications, deployment options, and GUI/Headless browsers. Travis supports all of the most popular databases: MySql, PostgreSql, MongoDB, CouchDB, and a myriad of others. It offers a number of notification options ranging from Email to IRC to HipChat (a chat service from Atlassian). Travis also offers deployment to just about every sort of provider there is, from Heroku to AWS S3 to RubyGems and also provides the ability to create custom web hooks to deploy to a provider not supported natively.

If at any point your project requires something that Travis does not support natively, you are given the permissions necessary to install any sort of libraries or services that can be installed with apt-get on an Ubuntu machine.

Travis requires that your projects be hosted on GitHub, but by doing so the setup is incredibly easy. You sign into Travis using your GitHub credentials and Travis pulls up all of your repositories automatically.

Getting a project running with Travis is fairly easy; you just create a yml file in your repository with certain lines pertaining to the language, needed services, commands to run, etc. We were able to set up everything we needed in six simple lines.

In order to get access to your private repositories, Travis offers several pricing plans, the cheapest of which is \$129 \cite{TravisPricing} for their ``Startup'' plan. That's a bit steep, but it does offer unlimited private repositories, unlimited collaborators, and two concurrent jobs.

From what we gathered, Travis appears to be targeted at companies, not individual developers. Travis requires you to host your projects on GitHub and only supports one process running at a time. However, Travis is incredibly easy to set up, does not require you to have your own server, comes with impressive built-in features, and works wonderfully if you are willing to open-source your repositories and put them on GitHub.

\subsubsection{Semaphore \cite{Semaphore}}
Semaphore is another online CI framework that connects to GitHub to bring in your projects. Semaphore is made by RenderedText, a software consulting team. Semaphore connects with your public and private repositories but requires a subscription after 30 days no matter which repositories you use.

Semaphore was originally designed for only Ruby applications but in January of 2014 they announced official support for Node.js and Javascript and as of February 26th they now offer official support for Clojure projects.\cite{SemaphoreBlog} These types of projects require no setup or files in your repository, Semaphore automatically detects project type and auto-fills build steps. Their ``supported stack'' page also lists C/C++, Java, Perl, and Python, but those must be configured manually.

Semaphore supports most databases and has a number of testing frameworks built-in. Once again you can use apt-get to install any missing libraries or dependencies. It would appear that deployment support is only available for Ruby projects.

@@

MagnumCI offers support for Ruby, PHP, Node.JS, and Go. MagnumCI, much like Semaphore, will attempt to auto-detect commands that it should run based on your project structure and language. All settings are overridable in a yml file if you choose.

@@

Where MagnumCI shines is in support of different repositories. MagnumCI offers support for pulling from GitHub, BitBucket, GitLab, and a few others. It does require a bit more setup to get your repositories connected, but what it comes down to is a couple lines of copied and pasted text within your repositories settings.

@@

Drone.io supports eleven languages including: C++, Dart, Go, Haskell, Java, Node.JS, Ruby, and others. Setup requires you to specify your language, as opposed to the automatic tools provided by the previous two CI frameworks, but will auto-generate built commands for you.

Drone.io offers support for all of the databases you'd want, has a variety of deployment options, and is entirely configurable from the online dashboard. It also offers the most browsers and headless browsers for use with web page testing tools such as Selenium and PhantomJS.

Drone.io is able to connect to GitHub, BitBucket, and Google Code respositories to get your projects automatically. Setup is simple, select the source of the repository (GitHub, BitBucket, or Google Code), select the repository from the list it gives you once it connects, select the language of the repository, edit the default build script, and you're ready to go.

Drone.io offers unlimited free open-source repositories. The next step up offers 5 private repositories for \$25 per month and for \$50 per month you get unlimited private repositories. They also offer higher tier plans that allow for concurrently running builds.

@@

\subsubsection{``A 2-Layer Model for the White-Box Testing of Web Applications'' \cite{2LayerModel}}
A couple of gentlemen at the Center for Scientific Research and Technology in Povo, Italy came with a model for white-box testing of web applications. (White box testing is when you access to the underlying code.) This paper breaks up the testing process into two abstraction levels, the navigation model, the way in which a webpage goes from page to page, and the control flow model, the way in which information is passed and stored on a given page or between pages. These constitute the 2-layers in the title. The navigation model represents high-level test cases, like asserting that a given link redirects to the correct location, while control flow represents low-level test cases, like making sure data is persisted between pages.

@@

\subsubsection{``Testing Web Applications in Practice'' \cite{TestingInPractice}}
Four students from the University of Seville, Spain published a paper with an overview of web testing. This paper was more of an introduction to testing, outlining the concepts of “Unit Testing”, “Integration Testing”, “Regression Testing”, testing the client versus testing the server, and a few others. It also describes how to test an actual web application using PHPUnit, a library similar to JUnit, for those of you familiar with Java. When writing their tests, they suggest taking more abstract actions and breaking them up into their functional parts and testing each of those. As an example, inserting a customer into the database (albeit not that abstract) is broken into tests for the function that inserts the customer and tests for making sure the customer makes it into the database.

@@

\subsubsection{``JAWS: A Javascript API for the Efficient Testing and Integration of Semantic Web Services'' \cite{JAWS}}
A researcher from Ford Motor Company published a paper regarding an API, called JAWS (Javascript, AJAX, Web Service), to facilitate testing and integration of Semantic Web Services. Semantic Web Services (SWS) are the server side of machine-to-machine interaction via the internet. This is opposed to machine-to-human interaction such as web pages that you visit personally. SWS use markup that is detailed and sophisticated which conforms to certain standards but is not human-readable.

@@

\subsubsection{``Testing Web Services: A Survey'' \cite{TestingWebServicesSurvey}}
Three researchers at the Centre for Research on Evolution, Search \& Testing at King's College in London wrote a survey of web frameworks for testing web services. Their focus is on Service-Oriented Computing, a paradigm in which web sites or applications provide small pieces of functionality usable by ``anyone''. These services are then combined to create more fully featured applications. What they note in particular is that when using web services, you rarely have access to the source code and must therefore black-box test them. Corollary to that is that you have to implicitly trust whoever made the service. They go through and discuss a number of frameworks and come to the conclusion that it's most certainly not a solved problem for the following reasons: The frequency of testing required, Testing without disrupting the operation of the service, Determining when testing is required and which operations need to be tested. Regarding the frequency of testing, web services often change in effort to make improvements, but those improvements can change the services and break tests. Testing without disrupting service is difficult because these services often limit accesses or simultaneous access of both a test and a running web application. Finally, determining when and what to test comes back to the trust issue. Some services provide their own testing metrics that include code coverage, number of tests, etc. But you have to trust that they are thoroughly testing whatever it may be.

>>>>

In the very beginning, web applications were easy to write and test because the only code was straight HTML with a common set of HTML tags. It didn't matter what browser was used to view the content because the viewer was always a home computer rendering plain HTML. As time progressed individual browsers began offering additional features and web applications became more rich but harder to test because the developer would need to run their code on a couple different browsers to make sure they all behaved similarly. In today's technological world, it is nearly impossible to run one's web application on all of the possible browser versions, configurations, and platforms that are available. Web applications are on home computers, phones, tablets, MP3 players, refrigerators \cite{SamsungFridge}, and a variety of other devices of varying sizes and capabilities. As a developer, one wants to target as many of those platforms as possible with a single code-base to save oneself time and effort. A naive developer might just release an application on all platforms and hope for the best, but releasing on all platforms without testing will likely drive consumers away if the application fails on their given platform.

@@

\subsubsection{Availability}
Web application are available anywhere there's internet. No need to install anything on a given device most of the time. Due to the ever-increasing popularity of mobile devices, most applications have both mobile and full versions of their software and so the application is ``with'' the user all the time.

\subsubsection{Multi-platform}
Very similar to the availability strength, web applications are platform independent. Whether the user is on their phone, tablet, laptop, or PC, the application only requires a web browser with certain functionality and in this day and age all devices come equipped with browsers that should have no problems.

@@

\subsubsection{What is the Client-side Portion?}
First, we'll address what a client is. The simple answer is: The User. The User's phone, computer, tablet, or other device communicating with a given website or application is the client. More specifically, the browser or service being using to communicate with the web is the client.

@@

\subsubsection{Unit Testing}
Unit testing is the testing of specific functions and functionality, or ``test units.'' Test units are ``A set of one or more computer program modules together with associated control data, [...] usage procedures, and operating procedures taht satisfy the following conditions: 1) All modules are from a single computer program. 2) At least one of the new or changed modules in the set has not completed the unit test. 3) The set of modules together with its associated data and procedures are the sole object of a testing process.'' \cite{UnitTestDefinition} Generally this means the testing of individual functions but can extend to a set of functions that produce a single module of functionality. What sets Unit Testing apart from other types of testing is that tests focus on one portion of the code or system rather than interactions between modules or the entire system.

@@

Unit tests are important because they are done in isolation from one another. The purpose of a unit test is to ensure that once individual modules are put together, the developer need only focus on the interaction between them instead of their individual functionality. Without the assurances of prior unit tests, integration would be a more stressful and mysterious proposition.

\subsubsection{Continuous Integration}
The original definition of Continuous Integration involves the idea of developers committing from their  branches to a master branch daily so that changes are continuously integrated in an effort to make sure all branches can, in fact, be integrated. It has since evolved into a more general idea of a tool that runs commands after each commit to a repository. This commands generally encompass running unit tests, integration tests, user interface tests, and also often publishing and disseminating notifications to interested parties. This is invaluable feedback because the developer can see if they're making progress in the right direction as they write code, as opposed to a situation in which the developer finishes coding and finds out they've made a bad assumption or decision between this commit and the last.

One of the most important aspects of a good piece of CI software is that it is automatic. There should be no need for a developer to do anything besides, perhaps, ``turn it on'' and start coding. As soon as a tool, CI or otherwise, requires more than one or two interactions to run, it becomes more of a nuisance and less of an asset.

\subsubsection{Acceptance Testing}
Acceptance testing is testing to confirm that the product meets a certain specification. Often this is making sure that the software meets an SRS (Software Requirements Specification) or a customer's outlined expectations. Often this testing is performed by the user of the software or customer that ordered the software, rather than the developers.

In an effort to automate this, some developers create ``User Stories'' which are automated tests that run a series of functions described by customers or an SRS. These User Stories are often written in a seperate language that is more like english than code. The traditional User Story template is: ``As a <role>, I want <goal/desire> so that <benefit>.'' For example: ``As a supervisor, I want to find my employees by their employee ID.'' These user stories are then broken down into more specific steps that can be automated.

@@

% NOT SURE I NEED THIS SECTION AT ALL
% \subsection{Assumptions and Requirements}
% In order to more thoroughly vet the many testing frameworks we came across, we had a number of assumptions about the projects we'd be looking at and requirements for those framework. 
%- Node.js server because it's JS, so it's testable.
%- Something to do unit testing
%- Something to do continuous integration

@@

\todo{THIS IS LAME}
Although there are multiple languages and tools available for creating a backing server, we chose Node.js because of it's wide use and because it is what we're most familiar with.

Javascript was chosen because it used in over 87\% of all websites. \cite{JSUsage}

@@

Web applications tend to keep track of users which most often constitutes the use of a database behind the scenes to store users and update them as necessary.

@@

\subsubsection{Tool Requirements}
\todo{Move this section elsewhere}
Our requirements for the selection of testing tools was relatively simple. In addition to meeting the requirements of our ``average web application'', the only other requirement was that the tool was free. What ``free'' means is that the developer would have access to at least the minimum functionality needed to use the tool on \emph{one} application that is \emph{open-source}. What we quickly found is that web testing tools love open-source projects but are far less willing to provide free functionality to private or closed-source projects.

Occasionally the cost of tools will be discussed but in general we did not review tools that did not offer a free option.
%- Free

@@

This relates to Jasmine is the way that the developer writes Jasmine tests. The idea behind jasmine tests is that they read, as much as possible, like english sentences. As an example, the following is a valid Jasmine test:
\begin{lstlisting}
describe("Arithmetic Test", function () {
  it("should be able to compute the addition of two numbers", function () {
    expect(1 + 2).toEqual(3);
  });

@@

Mocha also uses the ``describe -> it(\"should...\" '' patftern to create tests. There is no standard for writing expectation though, as each assertion library is likely to be slightly different.

Mocha's approach to asynchronous testing is quite a bit more straightforward than Jasmine's. In the ``it(...)'' anonymous function, there is passed an additional parameter called ``done'' which is then called when the asynchronous call has finished. This required us to edit the code we were testing to make all the async calls accept an additional callback, but it was a very small price to pay for extended testability. An example asynchronous test would look like this:
\begin{lstlisting}
describe("Asynch Mocha Test", function () {
  it("look like this", function (done) {
    myAsyncCall(param1, param2, function () {
      // This callback expected to run when async returns

@@

\subsubsection{QUnit \cite{QUnit}}
QUnit is an Assertion style framework developed by the jQuery Foundation, the makers of jQuery, an immensely popular framework for DOM manipulation and access. QUnit is a bit more developer-centered and not as ``feel-good'' as the other frameworks but has, so far, been the most easy to use and has the most thorough test reporting of any framework out of the box. Mocha and Jasmine show how many ``specs'', the ``it'' functions, have passed, which is great information, but QUnit takes it a step further and breaks down each spec into the asserts contained within:
\begin{Figure}
  \centering
  \includegraphics[width=\linewidth]{qunitrunner.png} 
  \captionof{figure}{Each individual spec is further broken down into the assertions within it.}
\end{Figure}
An interesting feature that QUnit has that we'd not seen elsewhere is the ability to specify how many assertions are expected to run in the test. This is incredibly useful for callbacks. By setting an expected number of assertions, tests can no longer fail silently just because an assertion was never run. If the QUnit test finishes and the assertion count is not what was specified, it will fail the test and let the developer know fewer assertions were called than expected.

@@

QUnit's handling of asynchronous tests is similar to Mocha's except instead of adding a parameter to the ``it'' function, the developer calls the ``asyncTest'' function instead. Finally, the developer calls ``start()'' when the asynchronous test is finished. Example:
\begin{lstlisting}
asyncTest("Async Test", function () {
  myAsyncCall(param1, param2, function () {
    // This callback expected to run when async returns

@@

\subsubsection{Intern\cite{InternIO}}
Intern is a hybrid unit testing and browser testing framework that aims to be an all-in-one testing framework. Intern has unit testing, browser testing, and code coverage information all built into the same tool. Intern runs on its own server which give it access to the internals of the project, but caused problems when attempting to interact with a seperate server running the Node.js application. We were unable to get the browser testing portion of Intern to work because of the inability to set up cross-server communication easily and properly.

%- TDD, BDD, Object methods
Intern uses Chai.js for assertion methods but has it built-in as opposed to Mocha in which the developer had to get it themselves. Again, this gives the developer access to Expect, Assert, and Object testing methods.

@@

%- Code Coverage!
Intern includes configurable code coverage metrics on tests by default. Running unit tests gives the number of lines covered (ran) by the tests. Code coverage is provided by another Javascript library, Istanbul, created by Krishnan Anantheswaran \cite{Istanbul}.

@@

Generally, all browser testing tools will be using Selenium behind the scenes and doing the housekeeping automatically. This is the case for both of the web testing tools that will follow this description.

@@

Tests are written as a long chain of function calls that produce an easy-to-read series of browser events. For example, the following code segment opens a browser, goes to google.com, makes some assertions, writes ``nightwatch'' in the search box, clicks the search button, and then makes a few more assertions:
\begin{lstlisting}
module.exports = {
  "Demo test Google" : function (client) {
    client
      .url("http://www.google.com")
      .waitForElementVisible("body", 1000)
      .assert.title("Google")
      .assert.visible("input[type=text]")
      .setValue("input[type=text]", "nightwatch")
      .waitForElementVisible("button[name=btnG]", 1000)
      .click("button[name=btnG]")
      .pause(1000)
      .assert.containsText("#main", "The Night Watch")
      .end();
  }
};
\end{lstlisting}
As one can see, just reading the code line by line paints a picture of exactly what is happening and what is being checked for. The same code in straight selenium is quite a bit more verbose.

@@

Though a small feature, Nightwatch has the ability to either assert or verify tests. The difference is that assertions will stop execution while verifications will merely log the failure and continue on. Verification can be useful if the developer wants to get an update on how many things are currently failing as opposed to having the entire test stop executing immediately after a single failure.

@@

Jenkins is a series of web pages that are set up to run on a given server. This is what it looks like:
\begin{Figure}
  \centering
  \includegraphics[width=0.95\linewidth]{jenkins.png}
\end{Figure}
Most companies give Jenkins a sub-domain on their web pages.

@@

Because Jenkins comes bare and runs on the system of the devloper's choosing, it can run any project that is set up. The downside is that there is no support out-of-the-box unless the system already has the necessary compilers, interpreters, applications, and/or libraries installed.

One of the exceptional strengths of Jenkins is that the developer is only limited by the hardware of the machine running Jenkins. Any increase in computing power will be directly usable by Jenkins. Jenkins can run as many jobs as the server can handle at one time.

@@

Jenkins is an exceptionally strong tool for CI, but requires immense overhead in setting up the environment to run a project in. However, once the server has the necessary applications and libraries, the builds and tests will run without issue. Jenkins can run an ``unlimited'' number of builds, tests, and processes with the only limiting factor the hardware that it is running on. It is also 100\% free and can connect with public and private repositories alike.

\subsubsection{Travis \cite{Travis}}
Travis is an online continuous integration framework with 29 members and 64 repositories at the time of this writing. Unlike Jenkins, Travis is all online and includes a dashboard from which the developer can monitor builds and processes. Travis has a free version which is fully-featured but requires the project to be open-source and a paid version which gives the deveoper more processing power and access to private repositories.

Travis comes with internal support for eleven different languages including Node.JS, Ruby, Java, and Python. Travis has incredibly thorough documentation and a wealth of built-in services to work with projects if needed. Theses services include databases, notifications, deployment options, and GUI/Headless browsers. Travis supports all of the most popular databases: MySql, PostgreSql, MongoDB, CouchDB, and a myriad of others. It offers a number of notification options ranging from Email to IRC to HipChat (a chat service from Atlassian). Travis also offers deployment to just about every sort of provider there is, from Heroku to AWS S3 to RubyGems and also provides the ability to create custom web hooks to deploy to a provider not supported natively.

If at any point the project requires something that Travis does not support natively, Travis gives the permissions necessary to install any sort of libraries or services that can be installed with apt-get on an Ubuntu machine.

Travis requires that projects be hosted on GitHub, but by doing so the setup is incredibly easy. The developer signs into Travis using GitHub credentials and Travis pulls up all of the developer's repositories automatically.

Getting a project running with Travis is fairly easy; just create a yml file in the repository with certain lines pertaining to the language, needed services, commands to run, etc. We were able to set up everything we needed in six simple lines.

In order to get access to private repositories, Travis offers several pricing plans, the cheapest of which is \$129 \cite{TravisPricing} for their ``Startup'' plan. That's a bit steep, but it does offer unlimited private repositories, unlimited collaborators, and two concurrent jobs.

From what we gathered, Travis appears to be targeted at companies, not individual developers. Travis requires developers to host their projects on GitHub and only supports one process running at a time. However, Travis is incredibly easy to set up, does not require it's own server, comes with impressive built-in features, and works wonderfully with open-source repositories on GitHub.

\subsubsection{Semaphore \cite{Semaphore}}
Semaphore is another online CI framework that connects to GitHub to bring in projects. Semaphore is made by RenderedText, a software consulting team. Semaphore connects with public and private repositories but requires a subscription after 30 days no matter which repositories are used.

Semaphore was originally designed for only Ruby applications but in January of 2014 they announced official support for Node.js and Javascript and as of February 26th they now offer official support for Clojure projects.\cite{SemaphoreBlog} These types of projects require no setup or files in the repository, Semaphore automatically detects project type and auto-fills build steps. Their ``supported stack'' page also lists C/C++, Java, Perl, and Python, but those must be configured manually.

Semaphore supports most databases and has a number of testing frameworks built-in. Once again any missing libraries or dependencies can be installed using apt-get. It would appear that deployment support is only available for Ruby projects.

@@

MagnumCI offers support for Ruby, PHP, Node.JS, and Go. MagnumCI, much like Semaphore, will attempt to auto-detect commands that it should run based on the project structure and language. All settings are overridable in a yml file.

@@

Where MagnumCI shines is in support of different repositories. MagnumCI offers support for pulling from GitHub, BitBucket, GitLab, and a few others. It does require a bit more setup to get repositories connected, but what it comes down to is a couple lines of copied and pasted text within the repositories' settings.

@@

Drone.io supports eleven languages including: C++, Dart, Go, Haskell, Java, Node.JS, Ruby, and others. Setup requires the developer to specify language, as opposed to the automatic tools provided by the previous two CI frameworks, but will auto-generate built commands.

Drone.io offers support for most of the databases we've heard of, has a variety of deployment options, and is entirely configurable from the online dashboard. It also offers the most browsers and headless browsers for use with web page testing tools such as Selenium and PhantomJS.

Drone.io is able to connect to GitHub, BitBucket, and Google Code respositories to get projects automatically. Setup is simple, select the source of the repository (GitHub, BitBucket, or Google Code), select the repository from the list it gives once it connects, select the language of the repository, edit the default build script, and the project is ready to go.

Drone.io offers unlimited free open-source repositories. The next step up offers 5 private repositories for \$25 per month and for \$50 per month, unlimited private repositories. They also offer higher tier plans that allow for concurrently running builds.

@@

\subsubsection{``A 2-Layer Model for the White-Box Testing of Web Applications'' \cite{2LayerModel}}
A couple of gentlemen at the Center for Scientific Research and Technology in Povo, Italy came with a model for white-box testing of web applications. (White box testing is when the developer is given access to the underlying code.) This paper breaks up the testing process into two abstraction levels, the navigation model, the way in which a webpage goes from page to page, and the control flow model, the way in which information is passed and stored on a given page or between pages. These constitute the 2-layers in the title. The navigation model represents high-level test cases, like asserting that a given link redirects to the correct location, while control flow represents low-level test cases, like making sure data is persisted between pages.

@@

\subsubsection{``Testing Web Applications in Practice'' \cite{TestingInPractice}}
Four students from the University of Seville, Spain published a paper with an overview of web testing. This paper was more of an introduction to testing, outlining the concepts of “Unit Testing”, “Integration Testing”, “Regression Testing”, testing the client versus testing the server, and a few others. It also describes how to test an actual web application using PHPUnit, a library similar to JUnit, for those developers familiar with Java. When writing their tests, they suggest taking more abstract actions and breaking them up into their functional parts and testing each of those. As an example, inserting a customer into the database (albeit not that abstract) is broken into tests for the function that inserts the customer and tests for making sure the customer makes it into the database.

@@

\subsubsection{``JAWS: A Javascript API for the Efficient Testing and Integration of Semantic Web Services'' \cite{JAWS}}
A researcher from Ford Motor Company published a paper regarding an API, called JAWS (Javascript, AJAX, Web Service), to facilitate testing and integration of Semantic Web Services. Semantic Web Services (SWS) are the server side of machine-to-machine interaction via the internet. This is opposed to machine-to-human interaction such as web pages that one visits personally. SWS use markup that is detailed and sophisticated which conforms to certain standards but is not human-readable.

@@

\subsubsection{``Testing Web Services: A Survey'' \cite{TestingWebServicesSurvey}}
Three researchers at the Centre for Research on Evolution, Search \& Testing at King's College in London wrote a survey of web frameworks for testing web services. Their focus is on Service-Oriented Computing, a paradigm in which web sites or applications provide small pieces of functionality usable by ``anyone''. These services are then combined to create more fully featured applications. What they note in particular is that when using web services, the developer rarely has access to the source code and must therefore black-box test them. Corollary to that is that the developer has to implicitly trust whoever made the service. They go through and discuss a number of frameworks and come to the conclusion that it's most certainly not a solved problem for the following reasons: The frequency of testing required, Testing without disrupting the operation of the service, Determining when testing is required and which operations need to be tested. Regarding the frequency of testing, web services often change in effort to make improvements, but those improvements can change the services and break tests. Testing without disrupting service is difficult because these services often limit accesses or simultaneous access of both a test and a running web application. Finally, determining when and what to test comes back to the trust issue. Some services provide their own testing metrics that include code coverage, number of tests, etc, but the developer must trust that the service is thoroughly tested, not just tested enough to provide interesting metrics.
